Turbulence in compact to giant HII regions

### 2021-09-10 strucfunc_paper.tex
Change name of main file
Load some more latex packages

@@

@@

\newcommand\halpha{H${\alpha}$}
\newcommand\n{[\ion{N}{II}]$\lambda$6584}
\newcommand\oi{[\ion{O}{III}]$\lambda$5007}
\newcommand\s{[\ion{S}{II}]$\lambda$6737}
\newcommand\si{$\sigma$}
\newcommand\kms{$^{-1}$}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/sigmas.pdf}
\caption{Log \(\sigma_{LOS}\) vs Log \(\sigma\) plot. The values are taken from Table \ref{tab:Res}. The solid-gray line indicate perfect correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}. The size of the markers indicate the distance to the region, the bigger the marker the farther the region. }
\label{fig:sigvssig}
\end{figure}

>>>>

\usepackage{savesym}
\savesymbol{tablenum}
\usepackage{siunitx}
\restoresymbol{SIX}{tablenum}

@@

\usepackage{xcolor}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

@@

\newcommand\halpha{H${\alpha}$}
\newcommand\n{[\ion{N}{II}]$\lambda$6584}
\newcommand\oi{[\ion{O}{III}]$\lambda$5007}
\newcommand\s{[\ion{S}{II}]$\lambda$6737}
\newcommand\kms{$^{-1}$}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/sigmas.pdf}
\caption{Log \(\sigma_{LOS}\) vs Log \(\sigma\) plot. The values are taken from Table \ref{tab:Res}. The solid-gray line indicate one-to-one correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}. The size of the markers indicate the distance to the region, the bigger the marker the farther the region. }
\label{fig:sigvssig}
\end{figure}
